---
title: "shinyNextUI"
format: md
---

<!-- index.md is generated from index.Rmd. Please edit that file -->

```{r, include = FALSE}
library(htmltools)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/index-",
  out.width = "100%"
)
```

<!-- badges: start -->
  [![R-CMD-check](https://github.com/RinteRface/shinyNextUI/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/RinteRface/shinyNextUI/actions/workflows/R-CMD-check.yaml)
  <!-- badges: end -->

The goal of `{shinyNextUI}` is to provide a wrapper around the
HeroUI React [library](https://www.heroui.com/).

## Notes

`{shinyNextUI}` is currently in alpha. Please carefully look at the current [issues](https://github.com/RinteRface/shinyNextUI/issues).

The current roadmap:

- Provide more aliases to match Shiny's vanilla notations like `selectInput`, ...
- Refine the navbar template.
- Allow to dynamically create [themes](https://nextui.org/docs/customization/theme).

`{shinyNextUI}` leverages tailwind css and some [rules](https://github.com/RinteRface/shinyNextUI/blob/main/js/src/output.css) have already been pre-compiled to use in the various [examples](https://github.com/RinteRface/shinyNextUI/tree/main/inst/examples). If you need custom styles, you can use the [`{windy}`](https://github.com/devOpifex/windy) package.

## Demo

```{r pokemon-demo, eval=FALSE, echo = TRUE}
library(shiny)
library(shinyNextUI)
library(shiny.react)

shinyAppDir(system.file("showcase", package = "shinyNextUI"))
```

```{r shinylive_url, echo = FALSE, results = 'asis'}
# extract the code from knitr code chunks by ID
code <- paste0(
  c(
    "webr::install(\"shinyNextUI\", repos = \"https://rinterface.github.io/rinterface-wasm-cran/\")",
    knitr::knit_code$get("pokemon-demo")
  ),
  collapse = "\n"
)

url <- roxy.shinylive::create_shinylive_url(code, header = FALSE)
```

```{r shinylive_iframe, echo = FALSE, eval = TRUE}
tags$iframe(
  class = "border border-5 rounded shadow-lg",
  src = url,
  width = "125%",
  height = "1200px"
)
```

## Installation

You can install the development version of `{shinyNextUI}` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("RinteRface/shinyNextUI")
```

## Example

To quickly get started with any example:

``` r
library(shinyNextUI)
# Get all examples
get_examples()
# Select an example and run the app
run_example("card")
```

## Developer

`{shinyNextUI}` leverages [tailwind](https://tailwindcss.com/) for the CSS management and [webpack](https://webpack.js.org/) as JS bundler and a mix between `{shiny.react}` and `{reactR}` for components and input management.

Within the `js` folder, run `npm install`. Then, for each change:

```shell
# Update CSS
npx tailwindcss -i ./src/input.css -o ./src/output.css --watch

# Change JS files
yarn webpack
```